Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-02-22 manuscript/manuscript.Rmd
Update manuscript.Rmd

# Non-standard evaluation
d <- distribution <- method <- mean_lambda <- sd_lambda <- NULL

@@

          for(method in c("box_cox", "yeo_johnson")){
            for(shift in c(FALSE, TRUE)){
              for(robust in c(FALSE)){
                # for(robust in c(FALSE, TRUE)){
                # Only 
                # Skip if robust, but not shifted.
                if(robust && !shift) next

@@

                yield(list(
                  "x" = x + d,
                  "d" = d,
                  "distribution" = distribution,
                  "method" = method,
                  "shift" = shift,
                  "robust" = robust,
                  "version" = version
                ))
              }
            }
          }
        }
      }
    })

  .compute_lambda <- function(parameter_set){
    # Create transformer object.
    transformer <- suppressWarnings(
      power.transform::find_transformation_parameters(
        x = parameter_set$x,
        method = parameter_set$method,
        robust = parameter_set$robust,
        shift = parameter_set$shift,
        lambda = NULL,
        optimiser_control = list("xtol_rel"=1e-3)))

    return(
      data.table::data.table(
        "distribution" = parameter_set$distribution,
        "method" = parameter_set$method,
        "version" = parameter_set$version,
        "d" = log10(parameter_set$d),
        "lambda" = transformer@lambda,
        "x_0" = transformer@shift
      ))
  }

@@

@@

@@

For conventional power transformations with a fixed shift parameter, the transformation $\phi^{\lambda, x_0} (\mathbf{X})$ may be substituted by $\phi^{\lambda} (\mathbf{X})$ in the definition of the Anderson-Darling criterion.

@@

>>>>

# Non-standard evaluation
d <- distribution <- method <- mean_lambda <- sd_lambda <- estimation_method <- NULL

@@

          for(method in c("box_cox", "yeo_johnson")){
            for(shift in c(FALSE, TRUE)){
              for(robust in c(FALSE)){
                for(estimation_method in setdiff(power.transform:::..estimators_all(), power.transform:::..estimators_raymaekers_robust())){

                  # Skip if robust, but not shifted.
                  if(robust && !shift) next

@@

                  yield(list(
                    "x" = x + d,
                    "d" = d,
                    "distribution" = distribution,
                    "method" = method,
                    "shift" = shift,
                    "robust" = robust,
                    "version" = version,
                    "estimation_method" = estimation_method
                  ))
                }
              }
            }
          }
        }
      }
    }
  )

  .compute_lambda <- function(parameter_set){
    # Create transformer object.
    if(parameter_set$version == "original"){
      transformer <- suppressWarnings(
      power.transform::find_transformation_parameters(
        x = parameter_set$x,
        method = parameter_set$method,
        robust = parameter_set$robust,
        shift = parameter_set$shift,
        estimation_method = parameter_set$estimation_method,
        lambda = NULL,
        optimiser_control = list("xtol_rel"=1e-5)))

    } else {
      transformer <- suppressWarnings(
      power.transform::find_transformation_parameters(
        x = parameter_set$x,
        method = parameter_set$method,
        robust = parameter_set$robust,
        shift = parameter_set$shift,
        estimation_method = parameter_set$estimation_method))
    }

    return(
      data.table::data.table(
        "distribution" = parameter_set$distribution,
        "method" = parameter_set$method,
        "estimation_method" = parameter_set$estimation_method,
        "version" = parameter_set$version,
        "d" = log10(parameter_set$d),
        "lambda" = transformer@lambda,
        "x_0" = transformer@shift
      ))
  }

@@

  # data <- lapply(
  #   X = experiments,
  #   FUN = .compute_lambda)

@@

# Only evaluate the MLE method here.
data <- data[estimation_method == "mle"]

@@

@@

## Optimisation using non-MLE criteria

Each of the criteria above can be used for optimisation, i.e.:

```{=latex}
\begin{equation}
\left\{ \hat{\lambda}, \hat{x}_0 \right\} = \argmin_{\lambda, x_0} U\left(\mathbf{X}, \lambda, x_0 \right)
\end{equation}
```

For conventional power transformations with a fixed shift parameter, the transformation $\phi^{\lambda, x_0} (\mathbf{X})$ may be substituted by $\phi^{\lambda} (\mathbf{X})$, or equivalently, $x_0$ is fixed:
```{=latex}
\begin{equation}
\left\{ \hat{\lambda}\right\} = \argmin_{\lambda} U\left(\mathbf{X}, \lambda; x_0 \right)
\end{equation}
```
